Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-02-25 paper/sec/formalization_neg_dep.tex
change explanation around NA formal def

Our formalization follows the definitions by Joag-Dev and Proschan~\cite{joagdev1983} closely.
% TODO: YK: I am struggling to understand the paragraph below.
% In reference to 2.1 in Joag-Dev/Proschan, do you mean they are missing the integrability conditions for f,g?
However, the authors did not correctly define the constraints for the possible set of test functions $f$ and $g$ in \cref{def:neg_assoc}, which does not make sense formally.
In the formalization, we assume that the functions are bounded and measurable.
On the other hand, we derive that the condition is still true, if $f, g$ are square-integrable.
Or alternatively integrable, and non-negative.
This is derived using the monotone-convergence theorem.

@@

Let us summarize a few key formalized results for negatively associated random variables used in our proof:

>>>>

Our formalization follows the definitions by Joag-Dev and Proschan~\cite{joagdev1983} closely.
However, their definition leaves the class of test functions $f$ and $g$ (in \cref{def:neg_assoc}) imprecise.
In particular, for the formalization, we limit these functions to those that are bounded and measurable.
Additionally, we provide elimination rules, showing that if $X_1,\dots,X_n$ are negatively associated, then the inequality on expectations is still true even if $f, g$ are only square-integrable; or, alternatively, integrable and non-negative. This is derived using the monotone-convergence theorem.

@@

Let us summarize a few key formalized results for negatively associated random variables used in our CVM proof:
